\minitoc

\vspace{0.5cm}
The second chapter focuses on the most fundamental decision unit of microeconomic theory: \textit{consumer}. The main reference is Chapter 2 and 3 of \citet{mas1995microeconomic}.

The basic setting of consumer demand study is \textit{market economy}, where the goods and services that the consumer may acquire and consume are available for purchase at known prices (or trade for other goods at know exchange rates).

In this chapter, we will focus on 2 major aspects of the consumer theory: choice and demand.
\begin{center}
    \begin{tabular}{rl}
    \hline
    \textbf{choice} & individual decision making analysis based on choice\\ 
    \textbf{demand} & individual decision making analysis based on preference \\ 
    \hline
    \end{tabular}
\end{center}

The starting point of individual decision problem is a \textit{set of possible (mutually exclusive) alternatives} from which the individual must choose. To model decision making process
on this set of alternatives, one can:
\begin{enumerate}
    \item[-] either start from the tastes, i.e., \textit{preference relations} of individuals, and set up the patterns of decision making with preferences
    \item[-] or, start from the actual actions of individuals, i.e. \textit{choices}, to deduct a pattern of decision making
\end{enumerate}

The two aspects of consumer theory are actually closely related to each other. Just like choices and preferences in Chapter 1, they are two sides of the same coin. However, they are NOT equivalent.
The major conclusion of choice-based consumer theory is WARP is essentially equivalent to the \textit{compensated law of demand}, but WARP imposes fewer restrictions on demand than preference-based theory,
hence, does NOT necessarily guarantee the existence of a rationalizing preference relation for consumer demand, therefore, \textit{strong axiom of revealed preference} is introduced.

\section{Basic setting}\label{chap2:sec1}
\input{chapter2/chapter2_sec1.tex}

\section{Choice Rules}\label{chap2:sec2}
%\input{chapter1/chapter1_sec2.tex}

\section{Linking Preferences with Choices}\label{chap2:sec3}
%\input{chapter1/chapter1_sec3.tex}

\section{Introducing Utility}\label{chap2:sec4}
%\input{chapter1/chapter1_sec4.tex}

\section{Commentary}\label{chap2:sec5}
%\input{chapter1/chapter1_sec5.tex}

\vspace{0.5cm}
\noindent\rule{\textwidth}{0.4pt}

For the content of this chapter, my main reference is Chapter 1 of \citet{mas1995microeconomic}. Section 1, Chapter 2 of \citet{kreps1990acourse} covers similar content but starts from strict preference $\succ$, it is a very
good complement to \citet{mas1995microeconomic}. Chapter 1 of \citet{kreps2013microeconomic} explores choice and preferences on infinite sets. Lecture 1 and 2 of \citet{ariel2012lecture} give a well organized, lecture-structured summary of
these contents, it is a very good read.