\documentclass[12pt,openany]{report}
\setlength{\headheight}{52pt}
\usepackage[a4paper,left=1in,right=1in,top=1in,bottom=1in, heightrounded, marginparwidth=2cm, marginparsep=3mm]{geometry}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\setlength{\parskip}{0.5em}
\usepackage{url}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\usepackage{palatino}
\usepackage{tocloft}
\usepackage[nottoc]{tocbibind}
\usepackage{marginnote}
\usepackage{multirow}
\usepackage{easybmat,bigdelim,arydshln}
\usepackage[authoryear,round]{natbib}
\usepackage{amssymb,amsmath,amsthm,amsfonts}
\usepackage{mathtools}
\usepackage{graphicx}
\graphicspath{{./chapter1/outputs/}}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{newpxtext,newpxmath}
\usepackage{fancyhdr}
\usepackage[Conny]{fncychap}
    \ChNameVar{\centering\huge\fontfamily{ppl}\selectfont\rm\bfseries}
    \ChNumVar{\huge\fontfamily{ppl}\selectfont}
    \ChTitleVar{\centering\LARGE\fontfamily{ppl}\selectfont\rm}

\usepackage{xcolor}

\hypersetup{
    colorlinks,
    citecolor=red,
    filecolor=black,
    linkcolor=violet,
    urlcolor=blue
}

\makeatletter
\newtheoremstyle{indented}
  {3pt}% space before
  {3pt}% space after
  {\addtolength{\@totalleftmargin}{3.5em}
   \addtolength{\linewidth}{-3.5em}
   \parshape 1 3.5em \linewidth}% body font
  {}% indent
  {\bfseries}% header font
  {.}% punctuation
  {.5em}% after theorem header
  {}% header specification (empty for default)
\makeatother

\theoremstyle{indented}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\numberwithin{definition}{section}
\numberwithin{theorem}{section}
\numberwithin{example}{section}

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\mdiff{\mathop{}\!\mathrm{D}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}

\renewcommand\cftchapafterpnum{\vskip5pt}
\renewcommand\cftsecafterpnum{\vskip0pt}

\fancypagestyle{mystyle}{%
  \fancyhf{}% Clear header/footer
  \renewcommand{\headrulewidth}{1pt}% Remove header rule
  \renewcommand{\footrulewidth}{1pt}% Remove footer rule
  \fancyhead[R]{\href{https://github.com/SaiChrisZHANG/MicroEconLearning}{Github Page}}
  \fancyhead[L]{Empirical Finance: A Review}
  \fancyfoot[L]{\hyperref[ToC-first-page]{To Contents}}
  \fancyfoot[C]{\small \leftmark}
  \fancyfoot[R]{\thepage}
}

\usepackage{minitoc}
\newcommand{\sidenotes}[1]{\marginnote{\raggedright\scriptsize#1}}

\usepackage{paralist}
  \let\itemize\compactitem
  \let\enditemize\endcompactitem
  \let\enumerate\compactenum
  \let\endenumerate\endcompactenum
  \let\description\compactdesc
  \let\enddescription\endcompactdesc
  \pltopsep=1pt
  \plitemsep=1pt
  \plparsep=1pt

\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\vspace{1pt}}
\AtEndEnvironment{quote}{\vspace{1pt}}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        
        \Huge
        \textbf{Microeconomic Theory I: A Notebook}

        \Large
        \textit{With Jonathan Libgober}
            
        \vspace{2.5cm}
        
        \LARGE    
        \textbf{Sai Zhang}
            
        \vfill
        
        \large    
        Check the \href{https://github.com/SaiChrisZHANG/MicroEconLearning}{Github Page} of this project, or \href{mailto:saizhang.econ@gmail.com}{email me}!

        \vspace{0.8cm}
        \large
        \today
            
    \end{center}
\end{titlepage}

%%%%%%%% Main content %%%%%%%%%%
%%%%%%%% Chapters are called separately %%%%%%%%%%

\chapter*{Here we go!}

This is my learning notebook of Microeconomic Theory I (Course number: ECON601 at USC Economics). As one of the core courses in 
an economic Ph.D. curriculum, Microeconomic Theory I is beyond important to my research. Therefore, I would love to use this notebook
as a commitment mechanism, to document lecture notes, discuss session and office hour intuitions, reading summaries, my personal questions
regarding the topics and more. By building a file from scratch, hopefull I could have a more systematic and sophisticated understanding on
the content of this course.

I thank Prof. Jonathan Libgober at USC Economics for leading the discussion of the course and providing intuitive ways to understand microeconomic theory.
Please check his webpage \href{https://www.jonlib.com/}{here}, he is such fun.

I also appreciate the time and effort my TA Qitong Wang put into this course, guiding me through discussing sessions and problem sets. When I have questions, he is 
always there to help.

Following the structure of the course, this notebook will cover three aspects of microeconomic theories: (a) individual decision making, (b) game theory, (c) mechanism design and contract theory. 
Apart from Jonathan's lecture notes, I will also summarize the reading materials, including: 
\cite{mas1995microeconomic}'s \textit{Microeconomic Theory}, \citet{mailath2018modeling}'s \textit{Modelling Strategic Behavior}\footnote{Latest version (May 2021) available \href{https://web.sas.upenn.edu/gmailath/books/modeling-strategic-behavior/}{here}.},
\cite{tirole1991game}'s \textit{Game Theory}, \cite{myerson1991game}'s \textit{Game Theory: Analysis of Conflicts}, \cite{bolton2005contract}'s \textit{Contract Theory}, 
\cite{Mailath2006repeated}'s \textit{Repeated Games and Reputation} and \cite{martin1994acourse}'s \textit{A Course in Game Theory}. Other materials will also be referred to along the way.


Building this notebook is truly a memorable journey for me. I would love to share this review and all the related
materials to anyone that finds them useful. And unavoidably, I would make some
typos and other minor mistakes (hopefully not big ones). So I'd really appreciate
any correction. If you find any mistakes, please send the mistakes to this email address \href{mailto:saizhang.econ@gmail.com}{saizhang.econ@gmail.com} or start a branch on \href{https://github.com/SaiChrisZHANG/MicroEconLearning}{Github}. BIG thanks in advance!

\newpage

\dominitoc
\phantomsection
\label{ToC-first-page}
\tableofcontents

\pagestyle{mystyle}
\part{Individual Decision Making}

\chapter{Preferences and Choices, Utilities}
\input{chapter1/chapter1.tex}

\chapter{Fundamentals of Consumer Theory}
\input{chapter2/chapter2.tex}

\chapter{Lagrange Maximization and Duality}
\input{chapter3/chapter3.tex}

\chapter{Stochastic Choice}

\chapter{Monotone Comparative Statics}

\chapter{Expected Utility and Decisionmaking under Uncertainty}

\chapter{Aggregation and the Existence of a Representative Consumer}

\chapter{Producer Theory}

\part{Game Theory}

\chapter{Nash Equilibrium and Bayesian Nash Equilibrium}

\chapter{Rationalizability and DOminant Strategies}

\chapter{Correlated Equilibrium}

\chapter{Dynamic Games and Refinements}

\chapter{Repeated Games/Folk Theorem}

\chapter{Recursive Methods in Repeated Games}

\part{Mechanism Design and Contract Theory}

\chapter{Arrow's Theorem and Social Choice}

\chapter{Boundaries of the Firm and Coase's Theorem}

\chapter{Implementation Concepts}

\chapter{The Revelation Principle}

\chapter{Auctions and Optimal Auctions}

\chapter{Efficient Implementation}

\chapter{Moral Hazard}

\chapter{Full Implementation}

\newpage
\bibliographystyle{plainnat}
\bibliography{ref.bib}

\end{document}