We start from the basic: \textit{weak preference relation}, $\succsim$.
\begin{definition}\label{def_succsim}
    A weak preference relation $\succsim$ on a set $X$ is a subset of $X\times X$. If $(x,y)\in \succsim \Rightarrow$ $x$ is at least as good as $y$, written as $x\succsim y$
\end{definition}

A weak preference relation will induce two other types of relations on $X$:
\begin{definition}\label{def_succ_and_sim}
    With $\succsim$ defined by Def. \ref{def_succsim}, we have
    \begin{enumerate}
        \item[-] the \textit{strict preference relation}, $\succ$ can be induced from $\succsim$ as: $x\succ y\Leftrightarrow x\succsim y \land y\not\succsim x$,
        or in words, $x$ if preferred to $y$.
        \item[-] the \textit{indifference relation}, $\sim$ can be induced from $\succsim$ as: $x\sim y \Leftrightarrow x\succsim y \land y\succsim x$, or in words, $x$ is indifferent to $y$.
    \end{enumerate}
\end{definition}

With the definition of these relations, we now define the central assumption of relations: \textit{\textbf{rationality}}. 
\begin{definition}\label{def_succsim_rational}
    A weak preference relation $\succsim$ is \textit{rational} if it is:
    \begin{enumerate}
        \item[-] Complete: $\forall x,y\in X$, $x\succsim y$ or $y\succsim x$ or both 
        \item[-] Transitive: $\forall x,y,z\in X$, $x\succsim y\land y\succsim z\Rightarrow x\succsim z$
    \end{enumerate}
\end{definition}

How to understand them? They are both strong assumptions:
\begin{enumerate}
    \item[-] Completeness of $\succsim$ means it is well-defined between any two possible alternatives. From the perspective of an individual, completeness means that she will make choices, and only meditated choices.
    \item[-] Transitivity of $\succsim$ implies that the decision maker will not have a preference cycle, since whoever has a preference cycle would suffer economically for it\footnote{There are 2 types of violations of 
    transitivity: irrational and mechanical. Irrational violations are easy to understand: decision makers simply do not follow transivity assumption, many reasons have been raised, including mental account, framing, menu effect, attraction effect, etc. Mechanical violations means that decision makers are "forced" to violate transitivity. One 
    example of this type of violation is aggregation of considerations: decision makers may aggregate several sub-preferences as together to make the choice, leading to violation of transitivity. Another example is when the preference
    is only defined for differences above a certain level (problem of perceptible differences). See \citet[Page 7-8]{mas1995microeconomic}, \citet[Page 4-5]{ariel2012lecture} for details}.   
\end{enumerate}

With the definition of rational $\succsim$ in Def. \ref{def_succsim_rational}, we can prove the following properites of $\succ$ and $\sim$ \textit{induced} by $\succsim$:
\begin{theorem} If $\succsim$ is rational, then:
    \begin{enumerate}
        \item[i.] $\succ$ is irreflexive ($x\succ x$ never holds) and transitive ($x\succ y \land y\succ z\Rightarrow x\succ z$)
        
        \underline{Proof}:
        \begin{enumerate}
            \item[-] irreflexive: by Def. \ref{def_succ_and_sim}, $x\succ x\Rightarrow x\succsim x \land x\not\succsim x$, self contracdiction.
            \item[-] transitive: $x\succ y \Rightarrow x\succsim y \land y\not\succsim x$, $y\succ z \Rightarrow y\succsim z \land z\not\succsim y$. By transitivity of $\succsim$, $x\succsim y\land y\succsim z\Rightarrow x\succsim z$. If $z\succsim x$, by transitivity of $\succsim$ and $x\succsim y$, we would have $z\succsim y$, contradicting $y\succ z$. Therefore $x\succsim z \land z\not\succsim x\Rightarrow x\succ z$. 
        \end{enumerate}
        \item[ii.] $\sim$ is reflexive ($x\sim x, \forall x$), transitive ($x\sim y\land y\sim z\Rightarrow x\sim z$) and symmetric ($x\sim y\Rightarrow y\sim x$)
        
        \underline{Proof}:
        \begin{enumerate}
            \item[-] reflexive: by completeness of $\succsim$, $\forall x, x\succsim x\Rightarrow x\sim x$
            \item[-] transitive: $x\sim y\Rightarrow x\succsim y \land y\succsim x$, $y\sim z\Rightarrow y\succsim z, z\succsim y$, by the transitivity of $\succsim$, we have $x\succsim z \land z\succsim x$, hen $x\sim z$
            \item[-] symmetric: $x\sim y \Rightarrow x\succsim y \land y\succsim x\Leftrightarrow y\succsim x \land x\succsim y\Rightarrow y\sim x$
        \end{enumerate}
        \item[iii.] $x\succ y\succsim z\Rightarrow x\succ z$ 
        
        \underline{Proof}: $x\succ y\Rightarrow x\succsim y\land y\not\succsim x$, hence $x\succ y\succsim z\Rightarrow x\succsim z$. If $z\succsim x$, by transitivity of $\succsim$, $y\succsim x$, contradicting $x\succ y$. Therefore, $z\not\succsim x$
    \end{enumerate}
\end{theorem}

We can also directly define a \textit{rational} $\succ$ (see \citet[Page 19-21]{kreps1990acourse}):
\begin{definition}\label{def_rational_succ}
    A strict preference ralation $\succ$ is rational if it is:
    \begin{enumerate}
        \item[-] asymmetric: $\nexists x,y\in X$ s.t. $x\succ y \land y\succ x$
        \item[-] negatively transitive: $x\succ y \Rightarrow \forall z\in X\setminus{x,y}$, $x\succ z\lor z\succ y \lor$both. 
    \end{enumerate}
\end{definition}

With Def. \ref{def_rational_succ} and Def. \ref{def_succsim_rational}, we can prove that $\succsim$ is rational iff $\succ$ is rational:
\begin{theorem}
    $\succsim$ is rational $\Leftrightarrow$ $\succ$ is rational, specifically:
    \begin{enumerate}
        \item[-] $\succsim$ is complete $\Leftrightarrow$ $\succ$ is asymmetric
        \item[-] $\succsim$ is transitive $\Leftrightarrow$ $\succ$ is negatively transitive
    \end{enumerate}
\end{theorem}

Proof:
\begin{description}
    \item[Step 1] proof $\succsim$ is rational $\Rightarrow$ $\succ$ 
    \begin{itemize}
        \item[-] \textbf{asymmetric}
        
        if $\exists x,y$ s.t. $x\succ y$ and $y\succ x$, then by the definition of induced strict preference, the pair $x,y$ must satisfy 
        $$\begin{cases}
        x\succsim y\text{ and }y\not\succsim x & (x\succ y)\\
        y\succsim x\text{ and }x\not\succsim y & (y\succ x)
        \end{cases}$$
        which is, by completeness of rational $\succsim$, impossible. Therefore, such pair $x,y$ don't exist. $\succ$ is proved to be asymetric.
        
        \item[-] \textbf{negatively transitive}
        
        First, $\forall z\notin\{x,y\}$, by completeness of rational $\succsim$, the relation between $x$ and $z$ is either $x\succsim z$ or $z\succsim x$.
        Similarly, the relation between $y$ and $z$ is either $y\succsim z$ or $z\succsim y$.
        
        Second, given $x\succ y$, $x,y$ satisfies $x\succsim y$ and $y\not\succsim x$.
        
        Also, it is easy to prove that: $x\succ y \land y\succsim z \Rightarrow x\succ z$, $x\succ y \land z\succsim x\Rightarrow z\succ y$; and $x\succ y\land z\sim x\Rightarrow z\succ y$, $x\succ y\land y\sim z\Rightarrow x\succ z$

        Now we have the following scenarios:
        \begin{enumerate}
        \item if $z\succsim x$ and $y\succsim z$, by transitivity of rational
        $\succsim$, $y\succsim x$, contradicting the definition of $x\succ y$.
        This scenario doesn't exist.
        \item if $x\succsim z$ and $y\succsim z$, since $x\succ y$, with the
        auxilary result proved above, we have $x\succ z$
        \item if $z\succsim x$ and $z\succsim y$, since $x\succ y$, with the
        auxilary result proved above, we have $z\succ y$
        \item if $x\succsim z$ and $z\succsim y$, since $x\succ y$, suppose:
        \begin{enumerate}
        \item $z\succsim x$ as well, then $x\sim z$, in this case $z\succ y$;
        \item $z\not\succsim x$, then $x\succ z$
        \item $y\succsim z$ as well, then $y\sim z$, in this case $x\succ z$
        \item $y\not\succsim z$, then $z\succ y$
        \end{enumerate}
        therefore, a complete summary of (a) to (d) would give:
        
        \begin{table}[h]
        \begin{centering}
        \begin{tabular}{ccc}
        \hline 
         & $z\succsim x$ & $z\not\succsim x$\tabularnewline
        \hline 
        $y\succsim z$ & $z\succ y$ \& $x\succ z$ & $x\succ z$\tabularnewline
        $y\not\succsim z$ & $z\succ y$ & $x\succ z$ \& $z\succ y$\tabularnewline
        \hline 
        \end{tabular}
        \par\end{centering}
        \end{table}
        
        \end{enumerate}
        Combining all above, we have proved negative transitivity of $\succ$.
        \end{itemize}
        With asymmetry and negative transitivity proved, we've proved that
        $\succsim$ is rational $\Rightarrow$$\succ$ is rational
        
\end{description}