Next, we approach the theory of decision making from choice behavior itself. Formally, choice behavior is represented by means of a \textit{choice structure} $(\mathcal{B},C(\cdot))$. Now, we define choice structure $(\mathcal{B},C(\cdot))$:
\begin{definition}
    A choice structure $(\mathcal{B},C(\cdot))$ has two ingredients:
    \begin{enumerate}
        \item[-] $\mathcal{B}\subset \mathcal{P}(X)\setminus\varnothing$, where $\mathcal{P}(X)$ is the power set of $X$. This means, every element $B\in \mathcal{B}$ is a subset of $X$\footnote{The elements $B\in\mathcal{B}$ are so-called \textit{budget sets}. The budget sets in $\mathcal{B}$ should be thought of as an exhaustive listing of all the choice experiments that can be achieved, but it is possible that some subsets of $X$ are not achievable.}.
        \item[-] $C(\cdot)$ is a \textit{choice rule correspondence} that assigns a nonempty set of chosen elements $C(B)\subset B$, $\forall B\in \mathcal{B}$\footnote{The choice set $C(B)$ can contain a single element, which is the choice among the alternatives in $B$. BUT, $C(B)$ can contain multiple elements, then elements of $C(B)$ are the \textit{acceptable alternatives} in $B$.}.
    \end{enumerate}
\end{definition}

Now we discuss the CORE assumption in this section: the Weak Axiom of Revealed Preference (WARP):
\begin{definition}
    A choice set $(\mathcal{B},C(\cdot))$ satisfies WARP if:
    \begin{enumerate}
        \item[-] $\forall B,B^{\prime}$ and $x,y\in B\cap B^{\prime}$, $x\in C(B),y\in C(B^{\prime})\Rightarrow x\in C(B^{\prime})$
    \end{enumerate}
\end{definition}

Or in words, WARP requires that if $x$ is chosen from some alternatives where $y$ is also available, then there can be NO budget set containing both $x$ and $y$
but only $y$ is chosen.

Following WARP, define the \textit{reveal preference relation} $\succsim^*$ as:
\begin{definition}\label{def_revealed_pref}
    Given a choice structure $(\mathcal{B},C(\cdot))$, $x\succsim^*y\Leftrightarrow \exists B\in\mathcal{B}$ s.t. $x,y\in B\land x\in C(B)$
\end{definition}
In words, $x$ is revealed at least as good as $y$.

With revealed preference defiend, we can rephrase WARP as: \textit{If x is revealed at least as good as y, then y \textbf{cannot} be revealed preferred to x}. Hence, $\succsim^*$ is not symmetric.

One thing to remember is that $\succsim^*$ need not be either complete or transitive. For $\succsim^*$ to be comparable, for a $B\in\mathcal{B}$ and $x,y\in B$, we must have either $x\in C(B)$, $y\in C(B)$ or both.

An example is:
\begin{example}
    Consider a choice structure $(\mathcal{B},C(\cdot))$ from $X=\{x,y,z\}$, where $\mathcal{B}=\{\{x,y\},\{x,y,z\}\}$. Under WARP, $C\{x,y\}=\{x\}\Rightarrow y\notin C\{x,y,z\}$.
    BUT, we can have $z\in C(\{x,y,z\})$.
\end{example}

This is why the induced preference is called \textit{revealed}: you don't know what else is going on.

There are 3 interesting properties of choice rules to keep in mind:
\begin{enumerate}
    \item[-] Property $\alpha$: $x\in A \subseteq B,x\in C(B)\Rightarrow x\in C(A)$.
    \item[-] Property $\beta$: $x,y\in C(A), A\subseteq B, y\in C(B)\Rightarrow x\in C(B)$
    \item[-] Property $\gamma$: $x\in C(B_1),x\in C(B_2) \cdots x\in C(B_n)\Rightarrow x\in C(B_1\cup B_2\cup\cdots\cup B_n)$
\end{enumerate}

For a rational preference relation $\succsim$, its induced choice function $C(\cdot,\succsim)$ satisfies the three properties:
\begin{enumerate}
    \item[$\alpha$:] For $x\in A \subseteq B,x\in C(B,\succsim)$, $x\succsim y, \forall y\in B$, and $A\subseteq B\Leftrightarrow \forall z\in A,z\in B$, hence $\forall z\in A,x\succsim z\Rightarrow x\in C(A,\succsim)$
    \item[$\beta$:] For $x,y\in C(A,\succsim), A\subseteq B, y\in C(B,\succsim)$, $x\succsim y$ and $\forall z\in B,y\succsim z$, by transitivity, $\forall z\in B, x\succsim z\Rightarrow x\in C(B,\succsim)$
    \item[$\gamma$:] $x\in C(B_i,\succsim),i=1,\cdots,n\Rightarrow \forall b^i_k \in B_i, x\succsim b_i\Rightarrow \forall b\in \{b^i_k\}, i=1,\cdots,n, x_i\succsim b_i\Rightarrow x\in C(B_1\cup B_2\cup\cdots\cup B_n,\succsim)$
\end{enumerate}

With Sen's $\alpha$ and $\beta$ defined, we have:
\begin{theorem}
    For a non-empty $C$, $C$ satisfies $\alpha$ and $\beta$ $\Leftrightarrow$ $C$ satisfies WARP
\end{theorem}

Now, let's prove this.
\begin{enumerate}
    \item[-] \textbf{Sen's $\alpha$ and $\beta \Rightarrow$ WARP}: Suppose $x,y\in A\cap B, x\in C(A), y\in C(B)$. Let $\tilde{A}=A\cap B$, since $\tilde{A}\subset A$ and $\tilde{A} \subset B$, Sen's $\alpha$ gives $x,y\in C(\tilde{A})$. Now we have $\tilde{A}\subset B, y\in C(B), x,y\in C(\tilde{A})$, by Sen's $\beta$, $x\in C(B)$. Thus, WARP holds.
    \item[-] \textbf{WARP $\Rightarrow$ Sen's $\alpha$ and $\beta$}: WARP gives $x,y\in A\cap B,x\in C(B), y\in C(A)\Rightarrow x\in C(A)$, in the special case of $A\subset B$, WARP will be reduced to Sen's $\alpha$ and $\beta$.\footnote{Another way of proving this is to introduce rationalizing preference relation (Def.\ref{def_rationalize_choice}). In fact, for $\mathcal{B}$ includes all subsets of $X$ of up to 3 elements, WARP $\Leftrightarrow$ $C$ is rationalizable $\Leftrightarrow$ Sen's $\alpha$ and $\beta$ are satisfied.}
\end{enumerate}